On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 blind.tex
Fix QED symbols (temp fix)

\begin{thm}
	\cref{proto:QPIP1Samp} has the same completeness and soundness guarantees as \cref{ProtoQPIP1}
\end{thm}
\begin{proof}
	A honest prover still gets accepted with overwhelming probability by the correctness of $\mathsf{QHE}$. \Ethan{Not sure if too hand-wavy}

@@

	In other words, anything a cheating prover can do after the compiliation, there exists a corresponding strategy in the version before.
	\Ethan {Ahhhh this is not rigorous at all}
\end{proof}

\begin{thm}
	\cref{proto:QPIP1Samp} is IND-CPA secure.
\end{thm}
\begin{proof}
	The only thing the prover gets is $\mathsf{QHE.Enc}_{pk}(x)$, $pk$, and $evk$. So this follows directly from the security of $\mathsf{QHE}$.
\end{proof}

>>>>

\begin{thm}
	\cref{proto:QPIP1Samp} has the same completeness and soundness guarantees as \cref{ProtoQPIP1}
\end{thm}
\begin{prf}
	A honest prover still gets accepted with overwhelming probability by the correctness of $\mathsf{QHE}$. \Ethan{Not sure if too hand-wavy}

@@

	In other words, anything a cheating prover can do after the compiliation, there exists a corresponding strategy in the version before.
	\Ethan {Ahhhh this is not rigorous at all}
\end{prf}

\begin{thm}
	\cref{proto:QPIP1Samp} is IND-CPA secure.
\end{thm}
\begin{prf}
	The only thing the prover gets is $\mathsf{QHE.Enc}_{pk}(x)$, $pk$, and $evk$. So this follows directly from the security of $\mathsf{QHE}$.
\end{prf}

### 2020-02-07 hamiltonian.tex
Fix missing dfns
Fix QED symbols (temp fix)

Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
\begin{thm}
	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
\end{thm}
\begin{proof}
	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
\end{proof}

Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
\begin{thm}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
	\end{itemize}
\end{thm}
\begin{proof}
	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
	$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
		$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$

@@

	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
	\begin{itemize}
		\item $C'$ uses only Hadamard and Toffoli gates.
		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
		\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
	\end{itemize}
\end{proof}

@@

\begin{thm}
	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients at most $O(\poly(T))$.
	Then \cref{AlgGroundStateCheck} accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
\end{thm}
\begin{proof}
	Here we follow \cite{PhysRevA.93.022326}.
	\begin{align*}
		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
	\end{align*}

	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
	\begin{align*}
		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
	\end{align*}
\end{proof}

>>>>

Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.
Which is significant because this gate set is a linear combinations of tensor products of $X$ and $Z$ operators:
\begin{thm}
	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
\end{thm}
\begin{prf}
	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
\end{prf}

Now we present the proof that $\set{H, \Lambda^2(X)}$ is indeed a universal gate set from \cite{quant-ph/0301040}: \Ethan{This definitely belongs in the appendix instead...}
\begin{thm}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
	\end{itemize}
\end{thm}
\begin{prf}
	We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
	$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
		$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$

@@

	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
	\begin{itemize}
		\item $C'$ uses only Hadamard and Toffoli gates.
		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
		\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
	\end{itemize}
\end{prf}

@@

\begin{thm}
	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients at most $O(\poly(T))$.
	Then \cref{AlgGroundStateCheck} accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
\end{thm}
\begin{prf}
	Here we follow \cite{PhysRevA.93.022326}.
	\begin{align*}
		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
	\end{align*}

	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
	\begin{align*}
		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
	\end{align*}
\end{prf}

### 2020-02-07 qpip.tex
Get lncs to compile
Fix QED symbols (temp fix)

\begin{observation}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

@@

\begin{thm}
    \label{QPIP1thm}
	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness. $\forall c\in\bbN$, it achieves soundness $(\varepsilon, \varepsilon)$ where $\varepsilon=T^{-c}$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{thm}
\begin{proof}
	It clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends to the verifier.

@@

	All errors up to this point is $O(\varepsilon)$.
\end{proof}

>>>>

\begin{lemma}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{lemma}
\begin{prf}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{prf}

@@

\begin{thm}
    \label{QPIP1thm}
	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness. $\forall c\in\bbN$, it achieves soundness $(\varepsilon, \varepsilon)$ where $\varepsilon=T^{-c}$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{thm}
\begin{prf}
	It clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends to the verifier.

@@

	All errors up to this point is $O(\varepsilon)$.
\end{prf}
